LogChunks: A Data Set for Build Log Analysis

### 2019-12-19 msr-paper/paper.tex
incorporate andys feedback from meeting

\author{Carolin Brandt}
\author{Annibale Panichella}
\author{Moritz Beller}

@@

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
Build failures are common in continuous integration (CI), but identifying the root cause of a failure is difficult.
To stimulate research in this area, we present \emph{LogChunks}, a collection of 797 Travis CI build logs from 80 GitHub repositories spread over 29 programming languages.
For each build log we manually labeled the log part (chunk) describing why the build failed.
We validated the data set by surveying the developers of the projects which produced the builds.
Various tools have been proposed to boil down verbose build logs to the specific lines valuable to the developer.
The width and depth of the \emph{LogChunks} data set makes it an ideal basis to benchmark build log analysis techniques.
Benchmarking different techniques will advance this research area and ultimately increase our understanding of CI build failures.
\end{abstract}

@@

\section{Introduction}
Continuous Integration (CI) has become a common practice in software engineering~\cite{hilton2016usage}.
Many software projects use CI~\cite{hilton2016usage,staahl2014modeling,beller2017oops} to detect bugs early~\cite{vasilescu2015quality,duvall2007continuous}, improve developer productivity~\cite{miller2008hundred,hilton2016usage} and communication~\cite{downs2012ambient}.
CI builds produce logs which report the results of the steps within the build.
These build logs contain a lot of valuable information for developers and researchers.
%Developers examine time measurement log statements to track how different stages of the build process perform.
%Researchers collect the commands triggering the build steps to reverse engineer the build configuration when only the log is available to them.
Both groups analyze build logs for descriptions of compiler errors, linter warnings or failed test notifications to uncover why a CI build failed~\cite{beller2017oops,seo2014programmers,vassallo2017a-tale}.

@@

We present \emph{LogChunks}, a collection of 797 Travis CI build logs from 80 GitHub repositories spread over 29 programming languages.
For each build log, we manually labeled which substring describes why the build failed.
The data set also provides keywords a developer would use to search for the labeled log chunk and categorizes the log chunks according to their format within the log.

@@

\paragraph{Evaluate Information (Chunk) Retrieval Techniques}
We created \emph{LogChunks} to evaluate and compare different techniques to retrieve information chunks from build logs \todo{cite journal paper (or preprint?)}.
The techniques we compared are based on program synthesis from examples, text similarity and searching for keywords.
In addition to that, \emph{LogChunks} can be the basis for evaluation and comparison of other chunk retrieval techniques.
For example, we can use the data set to investigate how reliable the diff and information retrieval approach of Amar et al.~\cite{amar2019mining} retrieves the reason the build failed.

@@

\paragraph{Analysis of Keywords Used to Search for Build Failure Descriptions}
\emph{LogChunks} provides keywords that a developer would look for to search the chunk describing why the build failed.
Analyzing these could help us understand how developers process build logs and which keywords a tool should use to mark an error description so developers quickly find it through text search.
We could also recommend users which search keywords they should use to find why the build failed.

@@

@@

For each repository, \emph{LogChunks} gives about 10 \texttt{Examples}.
Each \texttt{Example} consists of:
\begin{itemize}
	\item \texttt{Log:} the relative path to the input build log.
	\item \texttt{Chunk:} the log chunk that describes why the build failed.
	\item \texttt{Keywords:} keywords a developer would use to search for the log chunk.
	\item \texttt{Category:} a categorization of the structural representation of the log chunk within the build log.
				The category is relative to the other examples for the same repository.
\end{itemize}
Following, this section defines in more detail the labeled log chunk, search keywords and structural categories.

\begin{figure*}[htbp]
\centering
\begin{tabularx}{\textwidth}{@{}lXlX@{}}
  \toprule
  & Description & Unit & Example \\
  \midrule
  Log & relative path to the input build log & Path to Log File & Haskell/koalaman@shellcheck/failed/501296412.log \\
  Chunk & log chunk that describes why the build failed & String & shellcheck.hs:442:19: error:
    Variable not in scope: doesPathExist :: [Char] -> IO Bool \\ 
  Keywords & keywords a developer would use to search for the log chunk & Strings & Failures, FAILURE, FAILED \\ 
  Category & categorization of the structural representation of the log chunk within the build log & Integer & 0 \\
  \bottomrule
\end{tabularx}
\caption{Recommendations for each of the investigated chunk retrieval techniques}
\label{tab:single-technique-recommendations}
\end{figure*}

\paragraph{Chunk That Describes Why The Build Failed}
The \texttt{Chunk} is the substring of the build logs that describes why the build failed.
This can be the failing test case, the description of a failed linter rule or a compiler error.
The \texttt{Chunk} is one continuous string cut from the build log.
If there are multiple errors leading for the build to fail, the substring contains the first appearing continuous error descriptions.
\emph{Continuous} means that no lines reporting of normal build behavior are interrupting the error descriptions.
Wherever possible, it does \emph{not} include the log statements describing \emph{that} the build failed, but the description of \emph{why} it failed.
%For a few logs we were unable to define the section detailing why the build failed, e.g.\ because this information was logged in another log file.
%In these instances the \texttt{Chunk} contains the lines describing that the build failed.

\paragraph{Keywords}
The \texttt{Keywords} contain a list of one to three keywords appearing within the \texttt{Chunk} or in the area around it in the build log.
We aim to select keywords a developer would use to search for the \texttt{Chunk} when inspecting the build log.
Some example keywords from \emph{LogChunks} are: ``\texttt{FAIL}'', ``\texttt{Error}'', ``\texttt{failed}'', ``\texttt{[-]}'', ``\texttt{===================================}'' or ``\texttt{ERR!}''.

@@

@@

Of the 144 answers, 132 said our extraction was correct.
26 answered either ``close, but not quite correct'' or ``no, the build failed for another reason''.
We manually inspected these negative answers and found that some extractions were correct after all.
This yields 12 log extractions in our example set that were not correct.%, shown in Figure~\ref{fig:mails-extraction-correct}.

@@

Most of the initial incorrect answers we adjusted in the manual correction, stated that the proposed extraction did not show the whole description of why the build failed.
This is because we had to trim long labeled extractions to keep the mails readable.

@@

\section{Summary}
In this paper, we introduced the \emph{LogChunks} data set encompassing about 800 build logs from a wide range of projects using Travis CI\@.
For each log, we annotated the log chunk describing why the build failed and provide keywords a developer would use to search for the log chunk as well as a categorization of the log chunks according to their format within the log.
Still, there are limitations to our data set, which we present in the following.
We also propose several improvements and extensions to \emph{LogChunks}.
\label{sec:conclusion}

\paragraph{Chunk as One Consecutive Substring}
The manually labeled \texttt{Chunk} in our data set aims to contain the log part describing why the build failed.
However, it contains only one consecutive substring of the log text, whereas the reason a build failed could be described at multiple locations within the log.
We could improve this by extending \emph{LogChunks} to contain multiple substrings of the log text.

@@

>>>>

\author{Carolin Brandt}
\author{Annibale Panichella}
\author{Andy Zaidman}
\author{Moritz Beller}

@@

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
Build failures are common in continuous integration (CI), but identifying the root cause of a failure is difficult.
To stimulate research in this area, we present \emph{LogChunks}, a collection of 797 Travis CI build logs from 80 GitHub repositories spread over 29 programming languages.
For each build log we manually labeled the log part (chunk) describing why the build failed.
We validated the data set by surveying the developers of the projects which produced the builds.
Various tools have been proposed to boil down verbose build logs to the specific lines valuable to the developer.
The width and depth of the \emph{LogChunks} data set makes it an ideal basis to benchmark build log analysis techniques.
Benchmarking different techniques will advance the research area of build log analysis and ultimately increase our understanding of CI build failures.
\end{abstract}

@@

\section{Introduction}
Continuous Integration (CI) has become a common practice in software engineering~\cite{hilton2016usage}.
Many software projects use CI~\cite{hilton2016usage,staahl2014modeling,beller2017oops} to detect bugs early~\cite{vasilescu2015quality,duvall2007continuous}, improve developer productivity~\cite{miller2008hundred,hilton2016usage} and communication~\cite{downs2012ambient}.
CI builds produce logs which report the results of the steps within the build.
These build logs contain a lot of valuable information for developers and researchers.
%Developers examine time measurement log statements to track how different stages of the build process perform.
%Researchers collect the commands triggering the build steps to reverse engineer the build configuration when only the log is available to them.
They analyze build logs for descriptions of compiler errors, linter warnings or failed test notifications to uncover why a CI build failed~\cite{beller2017oops,seo2014programmers,vassallo2017a-tale}.

@@

Following Sim et al., creating a benchmark gives us the chance to ``increase the scientific maturity of the area''~\cite{sim2003using} of build log analysis.

We present \emph{LogChunks}, a collection of 797 Travis CI build logs from 80 GitHub repositories spread over 29 programming languages.
For each build log, we manually labeled which substring describes why the build failed.
The data set also provides keywords the authors would use to search for the labeled log chunk and categorizes the log chunks according to their format within the log.

@@

\paragraph{Benchmarking Build Log Analysis Techniques}
We created this data set to evaluate and compare different techniques to retrieve information chunks from build logs. %\todo{cite journal paper (or preprint?)}.
The techniques we compared are based on program synthesis from examples, text similarity and searching for keywords.
In addition to that, \emph{LogChunks} can be the basis for evaluation and comparison of other chunk retrieval techniques.
For example, we can use the data set to investigate how reliable the diff and information retrieval approach of Amar et al.~\cite{amar2019mining} retrieves the reason the build failed.

@@

\paragraph{Analysis of Keywords Used to Search for Build Failure Descriptions}
\emph{LogChunks} provides keywords that the authors would use to search for the chunk describing why the build failed.
Analyzing these could help us understand how users process build logs and which keywords a tool should use to mark an error description so developers quickly find it through text search.
We could also recommend users which search keywords they should use to find why the build failed.

@@

% Andy also proposed: automatic creation of issue reports on GitHub with extracted info: sounds okay, but build failures are to be fixed faster than a GH issue I would say

@@

For each repository, \emph{LogChunks} gives about 10 \texttt{Examples}.
Each \texttt{Example} consists of:
\begin{itemize}
	\item \texttt{Log:} the relative path to the input build log.
	\item \texttt{Chunk:} the log chunk that describes why the build failed.
	\item \texttt{Keywords:} keywords the authors would use to search for the log chunk.
	\item \texttt{Category:} a categorization of the structural representation of the log chunk within the build log.
				The category is relative to the other examples for the same repository.
\end{itemize}
Following, this section defines in more detail the labeled log chunk, search keywords and structural categories.

\begin{figure*}[htbp]
\centering
\begin{tabularx}{\textwidth}{@{}lXlX@{}}
  \toprule
  & Description & Unit & Example \\
  \midrule
  Log & relative path to the input build log & Path to Log File & Haskell/koalaman@shellcheck/failed/501296412.log \\
  Chunk & log chunk that describes why the build failed & String & shellcheck.hs:442:19: error:
    Variable not in scope: doesPathExist :: [Char] -> IO Bool \\ 
  Keywords & keywords the authors would use to search for the log chunk & Strings & Failures, FAILURE, FAILED \\ 
  Category & categorization of the structural representation of the log chunk within the build log & Integer & 0 \\
  \bottomrule
\end{tabularx}
\caption{Recommendations for each of the investigated chunk retrieval techniques}
\label{tab:single-technique-recommendations}
\end{figure*}

\paragraph{Chunk That Describes Why The Build Failed}
The \texttt{Chunk} is the substring of the build logs that describes why the build failed.
This can be the failing test case, the description of a failed linter rule or a compiler error.
The \texttt{Chunk} is one continuous string cut from the build log.
When the description \emph{why} the build failed was described in an external log, the \texttt{Chunk} includes the description \emph{that} the build failed.
%Wherever possible, it does \emph{not} include the log statements describing \emph{that} the build failed, but the description of \emph{why} it failed.
%For a few logs we were unable to define the section detailing why the build failed, e.g.\ because this information was logged in another log file.
%In these instances the \texttt{Chunk} contains the lines describing that the build failed.

\paragraph{Keywords}
The \texttt{Keywords} contain a list of one to three keywords appearing within the \texttt{Chunk} or in the area around it in the build log.
We selected keywords the authors would use to search for the \texttt{Chunk} within the build log after analyzing about 800 build logs manually.
Some example keywords from \emph{LogChunks} are: ``\texttt{FAIL}'', ``\texttt{Error}'', ``\texttt{failed}'', ``\texttt{[-]}'', ``\texttt{===================================}'' or ``\texttt{ERR!}''.

@@

% TODO Moritz: this is to answer questions 'why did you not do this standard thing': maybe there is a better position and/or way of saying this?
Calculating the standard measure for inter-rater agreement, Cohen's Kappa, is not applicable here.
For the log chunk it cannot represent the impact of overlapping selections of the labelers and for the keywords and structural categories the values the labelers could assign were not fixed.

@@

Of the 144 answers, 132 said our extraction was correct.
26 answered either ``close, but not quite correct'' or ``no, the build failed for another reason''.
We manually inspected these negative answers and found that some stated that the proposed extraction did not show the whole description of why the build failed.
This is because we had to trim long labeled extractions to keep the mails readable.
After adjusting these answers, 12 log extractions in our example set that were not correct.%, shown in Figure~\ref{fig:mails-extraction-correct}.

@@

@@

\section{Summary}
In this paper, we introduced the \emph{LogChunks} data set encompassing about 800 build logs from a wide range of projects using Travis CI\@.
For each log, we annotated the log chunk describing why the build failed and provide keywords a developer would use to search for the log chunk as well as a categorization of the log chunks according to their format within the log.

\emph{LogChunks} advances the research field of build log analysis by introducing a benchmark to rigorously examine research contributions~\cite{sim2003using}.

Still, there are limitations to our data set, which we present in the following.
We also propose several improvements and extensions to \emph{LogChunks}.
\label{sec:conclusion}

\paragraph{Chunk as One Consecutive Substring}
The manually labeled \texttt{Chunk} in our data set aims to contain the log part describing why the build failed.
However, it contains only one continuous substring of the log text, whereas the reason a build failed could be described at multiple locations within the log.
We could improve this by extending \emph{LogChunks} to contain multiple substrings of the log text.

@@

\paragraph{Validation of Search Keywords}
The keywords \emph{LogChunks} provides are based on the experience of the authors gained from analyzing about 800 build logs.
Next, we propose to evaluate whether these keywords would also be used by the actual project developers to find the log chunk describing why a build failed.
